Working title: Ecological network control

### 2018-05-19 paper/manuscript.Rmd
Improve legend figure controllability

```{r fig-example-networks, fig.width=fig_struct_control$width, fig.height=fig_struct_control$height, fig.cap="(a) To establish the direction of control we start with a weighted visitation network (on the right). In this network, the width of the links correspond to the frequency of visitation. We then calculate the dependencies between species pairs and create a directed network (left) in which the direction of the links correspond to the direction of the assymetry of their dependence. For instance, the population of plant $p_1$ is likely to be affected by the population of pollinator $a_1$ to a larger extent that the population of $a_1$ depends on $p_1$ because $a_1$ interacts more strongly with other species in the community; hence the direction of control between these two species can be simplyfied with a directed link from $a_1$ to $p_1$. (b) A system is structurally controllable if there are no inaccessible links or dilations. The network on the bottom left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously, in other workds there are less superiors ($x_2$) than subordinates ($x_1$ and $x_2$ ). The network in the bottom right  is not controllable because node $x_3$ is inaccessible from the input node $u_1$ in the system. Both systems can be made controllable by adding an extra input node (top)."}
replayPlot(fig_struct_control$plot)
```

>>>>

```{r fig-example-networks, fig.width=fig_struct_control$width, fig.height=fig_struct_control$height, fig.cap="Direction of control and controllability conditions. (a) To establish the direction of control we start with a weighted visitation network (on the left). In this network, the width of the links corresponds to the frequency of visitation between animals $a_i$ and plants $p_i$, with wider link indicating more visits. Plant $p_1$ is visited exclusively by $a_1$ but $p_1$ represents only a small fraction of the floral resources of $a_1$. Therefore the population of $p_1$ is more likely to be affected by $a_1$ than visceversa. We represent this with a directed link from $a_1$ to $p_1$ (right). The direction of control between all other species pairs can be similarly determined by inspecting the difference between their relative dependences. (b) Once we have established the directions of control we can determine wether the network is controllable or not. A system defined by a directed network (with state nodes $x_i$; species populations in an ecological context) and control inputs (nodes $u_i$, orange links) is structurally controllable if it satisfies two conditions: it has no dilations (expansions in the network) and no inaccessible nodes. The system on the top left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously, in other workds there are less superiors ($x_2$) than subordinates ($x_1$ and $x_3$). The network in the top right is not controllable because node $x_3$ is inaccessible for the only input node $u_1$ in the system. Both systems can be made controllable by adding an extra input node (top)."}
replayPlot(fig_struct_control$plot)
```
